---
title: '\textcolor{blue}{Assignment 1: R Programming}'
author: "\\textcolor{blue}{Sagar Kumar \t | \t194161013}"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---


```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```


**Importing Data from csvfile**
```{r}
df<-read.csv("xy.csv") #read data in csv file.
```

**x**  "independent variable"  
**y**  "dependent variable"  

**Data Set**
```{r}
df  #dataframe
```

**48 Observation**
Two Variables y is response variable and x is input variable.
\newpage

**Question 1**  

A simple least squares model y = B0+B1*x from first principles and obtain B0 and B1.  

```{r}
Y<-df$y #dependent Variable
intercept<-rep(1,length(Y)) #replicates the values.
#intercept
```

**Design Matrix**

```{r}
X<-as.matrix(cbind(intercept,df$x))
X  #Design Matrix
```


**Estmiating Coefficient**

```{r}
XtX_matrix<-solve(crossprod(X)) #crossprod ->X'X (inverse of X matrix)
#d_matrix
b=XtX_matrix  %*% crossprod(X,Y)  #Matrix Multiplication(%*%)
b
```

So **intercept** is: 3.128201  
and **slope** is :  2.005476


**Find B0 and B1 using the linear model package lm.**


```{r}

lm.fit<-lm(df$y~df$x,data=df) #lm function
coef(lm.fit)

```

So result is same .

\newpage

**Generate 100 values of x between [3:00; 50:00] and find the value
of y **

```{r}
random_no<-runif(100,3,50)  #Generate random no
random_no
```



```{r}
y=3.128+2.005*random_no
y #yvalues
```


